Advanced forensic Ext4 inode carving

### 2018-05-13 paper.tex
Abstract, intro and conclusion; more subsections

\maketitle
\begin{abstract}
Place an abstract here.
\end{abstract}

@@

\cite{braams:babel}

\section{The {\secit Body} of The Paper}

\subsection{Introduction to ext4}

@@

\subsubsection{The ext2 filesystem}

@@

\subsubsection{The ext3 file system}

@@

\subsubsection{The ext4 file system}

@@

\subsubsection{Comparison of ext4 and other Unix file systems}

@@

\subsection{File carving}

@@

\subsection{Evaluation of the proposed tool}

@@

\textit{Dataset}

@@

\textit{Search patterns and selectivity}

@@

\textit{Access rights}

@@

\textit{Timestamps}

@@

\textit{Number of hard links}

@@

\textit{Extent flag and header}

@@

\textit{File type}

@@

\textit{Pattern combination}

@@

\textit{Completeness and correctness}

@@

\textit{Real world cases}

@@

\textit{Overformatted file systems}

@@

\textit{Runtime performance}

@@

>>>>

\maketitle
\begin{abstract}
Many widely-used filesystems (NTFS, FAT, ext3) are well-researched in terms of digital forensics and data recovery, but this does not apply to ext4, a successor in the family of ext filesystems. Due to some new functionalities of ext4 and compatibility breaking, a novel approach for file carving had to developed. The advantages of this approach include its ability to restore files even in the case of a corrupted superblock. This article gives a summary of the original paper and its outcomes, also with an introduction to ext4 filesystem and ext family included.
\end{abstract}

@@

In the present, ext4 is a widely-used filesystem, especially on Linux-based operating systems and Android phones \cite{afeic}. The filesystem, released in 2008, has its origins in ext2 and ext3 filesystems. While many of their principles and structures were preserved (it is possible to upgrade from ext2 or ext3 in-place by setting new attributes), the changes are not just evolutionary. The way of storing and locating data blocks has changed, especially with the introduction of {\it extents}. From the forensical point of view, it was necessary to come up with new processes of recovering data.

This article provides a summary of the paper \cite{afeic}. But since the method is not easily understandable without wider information about ext4 way of working, we include here a description of the filesystem. Furthermore, a description of ext2 and ext3 must be also attached, as ext4 is closely tied to them and succeeds their functions.

Our work is organized in a following way: Section 1 is this introduction; Section 2 provides the description of the filesystems; Section 3 is the summary of the paper; in Section 4 results of the evaluation are described; and Section 5 is the conclusion.

\section{Introduction to ext filesystem family}

@@

\subsection{The ext2 filesystem}

@@

\subsection{The ext3 file system}

@@

\subsection{The ext4 file system}

@@

\subsection{Comparison of ext4 and other Unix file systems}

@@

\section{File carving in ext4}

@@

\section{Evaluation of the method}

@@

\subsection{Dataset}

@@

\subsection{Search patterns and selectivity}

@@

\subsubsection{Access rights}

@@

\subsubsection{Timestamps}

@@

\subsubsection{Number of hard links}

@@

\subsubsection{Extent flag and header}

@@

\subsubsection{File type}

@@

\subsubsection{Pattern combination}

@@

\subsubsection{Completeness and correctness}

@@

\subsection{Real world cases}

@@

\subsection{Overformatted file systems}

@@

\subsection{Runtime performance}

@@

In this article, we have introduced the readers to the structure and functioning of ext2, ext3 and ext4 filesystems. For ext4, we have presented a novel approach of data recovery, which is able to restore data even in case of a corrupted superblock \cite{afeic}. The solution was proved to be successful in many situations and was adapted for Sleuthkit framework.

In future work, the authors want to add backward compatibility, so even ext4 filesystems upgraded from ext3 would be also supported. This is not possible now, as only extents are considered, not (in)direct pointers, which initially remain in a converted ext4 filesystem.
